---
title: "tsfknn for forecasting timeseries using machine learning"
output:
  pdf_document: default
  html_notebook: default
---
source : [cran site](https://cran.r-project.org/web/packages/tsfknn/vignettes/tsfknn.html)

## Traditional methods
* ARIMA 
* exponential smoothing
both using forecast package

## ML methods
* artificial neurial networks (**nnfor package**)
* Gaussian process
* KNN


```{r}
install.packages("tsfknn")
```



## simple example 

h: number of future values to be predicted
lags: lagged values of the target used as features (1:2 - lagged values 1 and 2 should be used)
k: thenumber of nearest neighbours used by the KNN model

```{r}
ts = ts(1:88)
library(tsfknn)
pred <- knn_forecasting(ts, h = 1, lags = 1:20, k = 2)
knn_examples(pred)
```

```{r}
library(ggplot2)
autoplot(pred, highlight = "neighbors")
```

### multi-step ahead i.e. predicting more than one value

```{r}
pred <- knn_forecasting(USAccDeaths, h = 12, lags = 1:12, k = 2, msas = "MIMO")
autoplot(pred, highlight = "neighbors", faceting = FALSE)
```

### recursive strategy i.e. forecasting one but iteratively so you forcast many

```{r}
timeS <- window(UKgas, start = c(1976, 1))
pred <- knn_forecasting(timeS, h = 2, lags = 1:4, k = 2, msas = "recursive")
autoplot(pred, highlight = "neighbors")
```

## Selecting the K value

* start with - k to the squre troot of the number of trainin examples
* optimize k (slow)
*  use multiple k values and average the results

```{r}
pred <- knn_forecasting(ldeaths, h = 12, lags = 1:12, k = c(2, 4))
```

**you can also let the package to figre it out!!!**
__Just dont specifiy a value__

## Evaluating the model
```{r}
pred <- knn_forecasting(ts(1:20), h = 4, lags = 1:2, k = 2)
ro <- rolling_origin(pred, h = 4)
ro$global_accu
```

```{r}
pred <- knn_forecasting(ldeaths, h = 12, lags = 1:12)

```


# summary
```{r}
pred <- knn_forecasting(USAccDeaths, h = 12, lags = 1:12, msas = "MIMO")
#dont specifiy the k value,let the package identify it
autoplot(pred, highlight = "neighbors", faceting = FALSE)
ro <- rolling_origin(pred, h = 4)
ro$global_accu
```

